Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-08 R/survey_data_results.Rmd
file pathing update
Quick look at effect sizes used

pacman::p_load(dplyr,ggplot2)

# loading data
raw <- read.csv("./data/MA_CompPysio_Survey.csv")
metadata <- read.csv("./data/MA_CompPysio_Survey_metadata.csv")

@@

### Journals {.tabset .tabset-fade .tabset-pills}

```{r}
dat %>% dplyr::group_by(journal) %>% dplyr::tally() %>% dplyr::arrange(n) %>% dplyr::mutate(journal = factor(journal, levels = unique(journal))) %>% 
  ggplot() + tm + theme(axis.title.y = element_blank(),
                        axis.text.y = element_text(size=8)) +
  geom_col(aes(x = journal, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),breaks=seq(1,13,2)) +
  labs(x = "journal",
       y = "number of papers") +
  coord_flip()
```

@@

## R Session Information   
```{r}
print(sessionInfo(), locale = F)
```

>>>>

pacman::p_load(dplyr,ggplot2,here, pander, janitor)

# loading data
raw <- read.csv(here("data","MA_CompPysio_Survey.csv"))
metadata <- read.csv(here("data","MA_CompPysio_Survey_metadata.csv"))

@@

### Effect Sizes Used {.tabset .tabset-fade .tabset-pills}

```{r}
dat %>% dplyr::group_by(effect_size_type) %>% janitor::tabyl(effect_size_type) %>%
  dplyr::summarise(SMD = dplyr::if_else(grepl("SMD", effect_size_type), n, 0),
                  lnRR = dplyr::if_else(grepl("Response Ratio", effect_size_type), n, 0),
                    Zr = dplyr::if_else(grepl("correlation", effect_size_type), n, 0),
                 Other = dplyr::if_else(grepl("other|Q10", effect_size_type), n, 0),
                 Means = dplyr::if_else(grepl("mean/proportion/raw", effect_size_type), n, 0),
                 lnCVR = dplyr::if_else(grepl("lnCVR", effect_size_type), n, 0),
                 Slope = dplyr::if_else(grepl("slope", effect_size_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = n / sum(n)) %>% arrange(effect) %>% 
  ggplot() + tm + theme(axis.title.y = element_blank(),
                        axis.text.y = element_text(size=8)) +
  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
  labs(x = "Effect Size",
       y = "Number of Papers") +
  coord_flip()
```

@@

## R Session Information   
```{r}
pander(sessionInfo(), locale = FALSE)
```
